%-------------------------
% Resume
% Author : Dre Cura
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------


% \documentclass[letterpaper,11pt]{article}
\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\usepackage{setspace}

\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
\setstretch{1.5}

% set stretch (line spacing)

%-------------------------------------------
%%%%%%  Cover Letter Starts Here  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


Andre Cura

(647) 674-2715

ajlcura@gmail.com

\vspace{0.25in}

January 1, 2023

\vspace{0.25in}

Leap Corporation

\vspace{0.5in}

Dear Hiring Manager,

\vspace{0.5in}

I am pleased to be applying for the Web Developer position at Leap Corporation.
My production level experience with developing websites using React, HTML, CSS, and JavaScript ES6,
as well as my experience with developing mobile applications using React Native
matches well with your requirements.
In addition, my background with working in an agile software development environment
has given me the skills to adjust to changing dynamics
while meeting scheduled goals and deliverables.

\vspace{0.25in}

In my previous experience at Tasttlig Corporation,
I developed several web-based applications for the company.
These applications were used by the company's marketing teams,
local business partners, and customers
to host, manage, and avail content, including food festivals
to promote local restaurants in neighbourhoods.
I was involved in the design and development process for all applications,
and I managed enhancement requests after each rollout.

% \vspace{0.25in}
% 
% I am a proven team player, which is another important requirement for this position.
% I was recently voted by my peers to receive Tasttlig Corporation's
% Distinguished Developer Award for exhibiting ideal teamwork traits,
% including reliability, good communication, commitment, adaptability,
% and going above and beyond what is asked. Management also recognized
% my accomplishments in meeting project deliverable deadlines over 99\% of the time,
% exceeding expectations by 5\%.

\vspace{0.25in}

Thank you for taking the time to review my credentials.
I am very passionate about being a competent and contributing team player, and,
as a self-taught developer, I am always looking for opportunities to learn and grow.
% and I hope to have the opportunity to discuss my examples in greater detail with you.
I look forward to answering your questions and learning more about this position
and your development teams.

\vspace{0.5in}
Sincerely,

Andre Cura
\end{document}
