\documentclass[a4paper,12pt]{letter}
\usepackage{amsmath}

\makeatletter
\renewcommand\date[1]{\gdef\@date{\hbox to \linewidth{#1\hss}}}
\makeatother
\date{\today}

\begin{document}

\begin{letter}{Professor Marcelo Ponce Castro \\
Department of Computational and Mathematical Sciences \\
University of Toronto \\
1265 Military Trail \\
Toronto, ON M1C 1A4}

% \opening{Dear Prof.\ Estrada and Prof.\ Castro,}
\opening{Dear Professor Castro,}

I am writing to express my enthusiasm for the opportunity to become a Teaching Assistant for CSCB09 in the Department of Computational and Mathematical Sciences. With a strong foundation in C programming, extensive experience teaching the language to peers, and a passion for helping others learn, I am excited to contribute to the course and support the students in mastering this essential language.

I have a deep understanding of C, as I have studied it not only from an academic perspective but also from a practical, hands-on one. Having experience as a vulnerability researcher, I am well-versed in the internals of C and have spent significant time exploring its nuances. This experience has provided me with a unique ability to analyze and debug applications at a fundamental level—an essential skill in my field, which focuses on identifying vulnerabilities in programs written in languages like C. I think that it is valuable to know how things work and I am confident that I can help them understand the language and programming concepts at a deeper level.

Thank you for considering my application. I look forward to the opportunity to contribute to the success of CSCB09 and to make a meaningful impact on the students' educational experience. Please feel free to reach out if you would like any further information or references.

\closing{Warm regards,}
Andre John Louis Cura

\end{letter}

\end{document}
